\documentclass[]{article}

\title{Implementing Toolkit for Optimization under Uncertainty in OCaml}
 

\author{  {\bf David Tolpin} \\
Computer Science Dept. \\  
Ben-Gurion University \\ 
84105 Beer-Sheva, Israel \\ 
\and
 {\bf Solomon Eyal Shimony}  \\ 
Computer Science Dept. \\  
Ben-Gurion University \\ 
84105 Beer-Sheva, Israel \\ 
}


\begin{document} 
 
\maketitle 

\begin{abstract} 

We present a Toolkit for Optimization under Uncertainty, a framework for
development and deployment of meta-reasoning algorithms for parameter
optimization under uncertainty. The core code of the toolkit is written
in Objective CAML. We show how the power of the functional programming
language helped us to

\begin{itemize}
\item design and implement a compact language for definition
      of optimization problems by combining first-class functions with
      the traditional YACC-style parser specifications;
\item build a general problem domain-oriented structure and query
      it lazily according to the needs of each module using the powerful
      pattern matching capabilitie;
\item flexibly connect toolkit components using both covenient input
      and output formats and remote process communication via XML-RPC.
\end{itemize}

We compile the code with the INRIA's Objective Caml optimizing compiler
for performance or with the OCaml-Java compiler for easier deployment
with other tools and on different platforms. The toolkit can either be
used as a standalone environment for design and research of algorithms,
or linked to other code as a library for solving optimization problems.

The project artially supported by the IMG4 consortium under the MAGNET
program, funded by the Israel Ministry of Trade and Industry, and by
the Lynne and William Frankel center for computer sciences.

\end{abstract}
\end{document}
